Add Plant Functional Type (PFT) labels

### 2021-03-30 R/add_plant_functional_type.Rmd
display table and write to csv

```{r message=FALSE}
library(tidyverse)
library(here)
library(dplyr)
```

@@

for(i in 1:nrow(taxon_pft_lookup)){
  # print row and current genusSpecies label
  print(i)
  genusSpecies <- taxon_pft_lookup$genusSpecies[i]
  print(genusSpecies)

@@

  # For taxons not described in this code, set their PFT to unknown
  else print("PFT unknown")

  # print corresponding PFT
  print(taxon_pft_lookup$pft[i])
}

@@

>>>>

```{r message=FALSE}
library(tidyverse)
library(here)
library(dplyr)
library(kableExtra)
```

@@

for(i in 1:nrow(taxon_pft_lookup)){
  # print row and current genusSpecies label
  #print(i)
  genusSpecies <- taxon_pft_lookup$genusSpecies[i]
  #print(genusSpecies)

@@

  # For taxons not described in this code
  #else #print("PFT unknown")

}

@@

```{r}
kableExtra::kable(taxon_pft_lookup) %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r}
# write the lookup table to a csv 
write_csv(x = taxon_pft_lookup,
          file = here::here("R","output","taxon_pft_lookup.csv"))
```
